### 2023-06-26 manuscript.tex
footnotes [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/51ed4a0f879b511074d60b75dcd5ef10837b4eba.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/51ed4a0f879b511074d60b75dcd5ef10837b4eba/checks
https://github.com/stain/2022-fdo-paper/actions/runs/5381976871

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/cbf2f8a9960d492b42521c3808995ff47b2311f3/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/cbf2f8a9960d492b42521c3808995ff47b2311f3}{stain/2022-fdo-paper@cbf2f8a}
on June 26, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/51ed4a0f879b511074d60b75dcd5ef10837b4eba/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/51ed4a0f879b511074d60b75dcd5ef10837b4eba}{stain/2022-fdo-paper@51ed4a0}
on June 26, 2023.
